Adaptive evolution with aneuploidy and mutation

### 2022-06-07 ms/ms.tex
update FA results

This result is not unique to the MAP parameter estimate. 
We simulated genotype frequency dynamics using parameter samples from the posterior distribution (\Cref{fig:posterior}), and computed the posterior distribution of $F_A$ (\Cref{fig:ppc-plot}B). 
The mean $F_A$ was just 0.1675 [0.0142 - 0.3758 95\% CI] and only in 408 of 86,349 posterior samples (0.47\%) $F_A$ was  larger than 0.5, that is, \eumt\ was more likely to arise from an aneuploid cell.  
Thus, if we pick up a cell from the evolved \eumt\ population, it is more likely to have descended directly from an euploid cell than from an aneuploid cell.
The probability of \eumt\ descending from \anwt\ ($F_A$) increases with the aneuploidy rate, $\delta$, and decreases with the mutation rate, $\mu$, and in some cases can also be affected by the fitness parameters (\Cref{fig:ppc-plot}C and \Cref{fig:fig:posterior_FA_supp}).

@@

% FIG posterior F_A supplementary
\begin{figure}[p]
	\begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/scatter100000_rater_fitr_from_wt.pdf}      
	\end{subfigure}
	  \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/scatter100000_rater_fitr_mut.pdf}
  \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/scatter100000_rater_means_log.pdf}
    \end{subfigure}    
  \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/scatter100000_rater_means.pdf}
  \end{subfigure}
	\caption{\textbf{Posterior distribution of $F_A$.}
	\textbf{(A,B)} $F_A$ values (color coded) as in \Cref{fig:ppc-plot} for different parameter choices on the x- and y-axes. White start denotes the MAP estimate.
	\textbf{(C,D)} $F_A$ values (y-axis) as a function of $\delta/\mu$, the aneuploidy-to-mutation rate ratio.
	}
    \label{fig:posterior_FA_supp}
\end{figure}

>>>>

This result is not unique to the MAP parameter estimate. 
We simulated genotype frequency dynamics using parameter samples from the posterior distribution (\Cref{fig:posterior}), and computed the posterior distribution of $F_A$ (\Cref{fig:ppc-plot}B). 
The mean $F_A$ was just 0.1675 [0.0142 - 0.3758 95\% CI] and only in 408 of 86,349 posterior samples (0.47\%) $F_A$ was  larger than 0.5, that is, \eumt\ was more likely to arise from an aneuploid cell.  
Thus, if we pick up a cell from the evolved \eumt\ population, it is more likely to have descended directly from an euploid cell than from an aneuploid cell.
The probability of \eumt\ descending from \anwt\ ($F_A$) increases with the aneuploidy rate, $\delta$, and decreases with the mutation rate, $\mu$, and in some cases can also be affected by the fitness parameters (\Cref{fig:ppc-plot}C and \Cref{fig:posterior_FA_supp}).

@@

% FIG posterior F_A supplementary
\begin{figure}[p]
	\begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/scatter100000_rater_fitr_from_wt.pdf}      
	\end{subfigure}
	  \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/scatter100000_rater_fitr_mut.pdf}
  \end{subfigure}
    \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/scatter100000_rater_means_log.pdf}
    \end{subfigure}    
  \begin{subfigure}{0.5\textwidth}
      \centering
      \includegraphics[width=\textwidth]{../figures/plot_rateratios_means.pdf}
  \end{subfigure}
	\caption{\textbf{Posterior distribution of $F_A$.}
	\textbf{(A,B)} $F_A$ values (color coded) as in \Cref{fig:ppc-plot} for different parameter choices on the x- and y-axes. White start denotes the MAP estimate.
	\textbf{(C,D)} $F_A$ values (y-axis) as a function of $\delta/\mu$, the aneuploidy-to-mutation rate ratio.
	}
    \label{fig:posterior_FA_supp}
\end{figure}
